19Q2

### 2019-10-09 19Q2.Rmd
update Rmd

```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
# g2p_dg_counts[g2p_dg_counts == 0] <- NA

g2p_gene_order <- colnames(g2p_dg_counts)
g2p_drug_order <- rownames(g2p_dg_counts)

# Create annotation layer
hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), "Screened", "Not screened")
hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), "Screened", "Not screened")
hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), "Screened", "Not screened")
rownames(hta_data) <- hta_data$Drug
hta_data$Drug <- NULL

@@

```{r auc_clustered_ht, eval=TRUE}
ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
ctrp_auc_grid <- dcast(ctrp, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
gdsc_auc_grid <- dcast(gdsc, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)

@@

```{r protein_change_data}
ccle_prot <- filter(prot, Database == "CCLE")
ccle_prot <- unfactorize(ccle_prot)
# ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)

@@

```{r prot_wilcoxon_tests, eval=FALSE}
ccle_prot <- unfactorize(ccle_prot)
ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")

@@

```{r fusion_data}
ccle_fus <- filter(fus, Database == "CCLE")
ccle_fus <- unfactorize(ccle_fus)

@@

ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ccle_fus_boxplot
# ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")

@@

ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ctrp_fus_boxplot
# ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")

@@

gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
gdsc_fus_boxplot
# ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
```

@@

>>>>

```{r g2p_gount_summ}
g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
# g2p_dg_counts[g2p_dg_counts == 0] <- NA

g2p_gene_order <- colnames(g2p_dg_counts)
g2p_drug_order <- rownames(g2p_dg_counts)
```

```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
# Create annotation layer
hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), "Screened", "Not screened")
hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), "Screened", "Not screened")
hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), "Screened", "Not screened")
rownames(hta_data) <- hta_data$Drug
hta_data$Drug <- NULL

@@

```{r auc_clustered_ht, eval=FALSE}
ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
ctrp_auc_grid <- dcast(ctrp, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
gdsc_auc_grid <- dcast(gdsc, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)

@@

```{r protein_change_data}
crispr_prot <- unfactorize(crispr_prot)

ccle_prot <- filter(prot, Database == "CCLE")
ccle_prot <- unfactorize(ccle_prot)
# ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)

@@

**10/9 ENDED HERE**

```{r prot_wilcoxon_tests, eval=FALSE}
# crispr_prot <- unfactorize(crispr_prot)
# crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
# 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
# crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")

ccle_prot <- unfactorize(ccle_prot)
ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")

@@

```{r fusion_data}
crispr_fus <- unfactorize(crispr_fus)

ccle_fus <- filter(fus, Database == "CCLE")
ccle_fus <- unfactorize(ccle_fus)

@@

ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ccle_fus_boxplot
ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")

@@

ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ctrp_fus_boxplot
ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")

@@

gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
gdsc_fus_boxplot
ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
```

@@

**10/9 STOPPED HERE BEFORE REALIZING I NEEDED TO RUN CRISPR PROT AND FUS WILCOXON TESTS**
